Covariate analysis of UFL-Mayo-ISB RNASeq reprocessed counts (both cerebellum and temporal cortex)

### 2016-05-29 code/Rmd/Mayo_RNASeq_Reprocessed.Rmd
Added markdown to process reprocessed RNASeq from Mayo brain bank data

---
title: "Covariate analysis of UFL-Mayo-ISB RNASeq (both cerebellum and temporal cortex) samples from MayoBrainBank_Dickson alone"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(knit2synapse)
library(synapseClient)
library(knitr)
library(githubr)

@@

knit2synapse::knitToFolderEntity(file = "./Mayo_MayoBrainBankDickson_RNASeq.Rmd",
                                 parentId = "syn5570325",
                                 entityName = 'UFL_Mayo_ISB Mayo Brain Bank Dickson RNASeq')
```

@@

library(doParallel)
library(foreach)

cl = makeCluster(14)
registerDoParallel(cl)

## Requires ggdendro
devtools::source_url("https://raw.githubusercontent.com/chr1swallace/random-functions/master/R/ggplot-heatmap.R")

# source utility files from ../R/lib folder
file.sources = list.files('../R/lib',pattern="*.R", full.names=T)
tmp = sapply(file.sources,source,.GlobalEnv)

@@

thisFileName <- 'Mayo_MayoBrainBankDickson_RNASeq.Rmd'

# Github link
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='AMPAD')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
# Download expression data
COUNT_TC_ID <- 'syn4650257';
ALL_USED_IDs <- COUNT_TC_ID
COUNT_TC <- read.table(synGet(COUNT_TC_ID)@filePath, header=T, sep='\t', check.names = F)

# Download expression data
COUNT_CE_ID <- 'syn5201012';
ALL_USED_IDs[length(ALL_USED_IDs)+1] <- COUNT_CE_ID
COUNT_CE <- read.table(synGet(COUNT_CE_ID)@filePath, header=T, sep='\t', check.names = F)

COUNT = plyr::join_all(list(COUNT_TC, COUNT_CE)) %>%
  as.data.frame

@@

### Data preprocessing
```{r preprocess.data,cache=FALSE, echo=TRUE}
# Fix metadata
METADATA$AgeAtDeath = gsub("_or_above", "", METADATA$AgeAtDeath)
METADATA$Diagnosis = gsub("Pathologic Aging","Pathologic_Aging", METADATA$Diagnosis)
METADATA$BrainRegion.Diagnosis = paste(METADATA$BrainRegion, METADATA$Diagnosis, sep = '.')
METADATA$RIN2 = METADATA$RIN^2
METADATA <- METADATA %>%
  dplyr::filter(!(ID %in% c("742_CER", "11386_CER","11311_CER","1923_CER","11477_CER", "11344_CER", 
                            "1923_TCX", "11423_TCX", "1940_TCX", "7095_TCX", "11408_TCX"))) %>%
  filter(Source == 'MayoBrainBank_Dickson')
```
Following samples were considered outliers and removed based on PCA and/or eucledian distance:
```{r preprocess.data1}
# Match covariates to expression data
indToRetain = intersect(METADATA$ID, colnames(COUNT))

COUNT <- COUNT[, c('ensembl_id', intersect(colnames(COUNT), indToRetain))]

rownames(METADATA) = METADATA$ID
METADATA = METADATA[rownames(METADATA) %in% indToRetain,]

COUNT = COUNT[, c('ensembl_id', indToRetain)]
METADATA = METADATA[indToRetain,]

rownames(COUNT) = COUNT$ensembl_id
COUNT$ensembl_id = NULL
```
`r dim(COUNT)[2]` samples from `r length(unique(METADATA$Donor_ID))` subjects were obtained from the Mayo cohorts in AMP-AD portal

@@

### Covariate clustering
Determine relationship between covariates. 
```{r covariates.clustering}
FactorCovariates <- c("Donor_ID", "Gender", "FLOWCELL", "BrainRegion.Diagnosis")
ContCovariates <- c("RIN", "RIN2", "AgeAtDeath")

@@

Clustering of initial normalised data (with NULL design)
```{r decompse.normalise.data1, fig.height=15, fig.width=10, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(VOOM.GENE_EXPRESSION$E)

@@

WGCNA::plotDendroAndColors(sampleTrees, 
                           labels2colors(cbind(tree,COVARIATES.tmp)),
                           groupLabels = c('Cluster',colnames(COVARIATES.tmp)))
dev.off()

tmp = paste('Samples in cluster 0 are', paste(sampleTrees$labels[tree == 0], collapse = ','))
tmp = base::gsub('_','\\\\_',tmp)
writeLines(tmp)
tmp = paste('Samples in cluster 3 are', paste(sampleTrees$labels[tree == 3], collapse = ','))
tmp = base::gsub('_','\\\\_',tmp)
writeLines(tmp)
```
### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates is used to find significant covariates
```{r preAdjusted.covariates, results='asis', echo=FALSE}
# Find correlation between PC's of gene expression with covariates
preAdjustedSigCovars = runPCAandPlotCorrelations(VOOM.GENE_EXPRESSION$E, COVARIATES,
                                                 'NULL design(voom-normalized)',
                                                 isKeyPlot=TRUE)

@@

### Sanity Check
Residualise significant covariates using a linear model and find correlation between PCA of residuals with covariates
```{r residualSigCovars.ALL, fig.width=25, fig.height=12}
residualSigCovars[["PC_res"]][[2]]$plotData
```
Adding "BrainRegion.Diagnosis" back to the residuals
```{r addVarsBack}
varsToAddBackIn <-  grep("BrainRegion.Diagnosis", colnames(FIT$coefficients), value = T)
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION + 
  t(data.matrix(DM1$design[,varsToAddBackIn]) %*% t(FIT$coefficients[,varsToAddBackIn]))
RESIDUAL.GENE_EXPRESSION = rownameToFirstColumn(RESIDUAL.GENE_EXPRESSION, 'ensembl_gene_id') 
```

### Clustering residual gene expression
```{r decompse.normalise.data3, fig.height=10, fig.width=9, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(RESIDUAL.GENE_EXPRESSION[,-(1)], scale.=T)

@@

tmp = paste('Samples in cluster 0 are', paste(sampleTrees$labels[tree == 0], collapse = ','))
tmp = base::gsub('_','\\\\_',tmp)
writeLines(tmp)
tmp = paste('Samples in cluster 3 are', paste(sampleTrees$labels[tree == 3], collapse = ','))
tmp = base::gsub('_','\\\\_',tmp)
writeLines(tmp)
tmp = paste('Samples in cluster 4 are', paste(sampleTrees$labels[tree == 4], collapse = ','))
tmp = base::gsub('_','\\\\_',tmp)
writeLines(tmp)
```

@@

# Query biomart
Ensemble2HGNC <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol"),
                       filters = "ensembl_gene_id", values = RESIDUAL.GENE_EXPRESSION$ensembl_gene_id,
                       mart = mart)
RESIDUAL.GENE_EXPRESSION <- left_join(RESIDUAL.GENE_EXPRESSION, Ensemble2HGNC) %>%
  dplyr::select(ensembl_gene_id, hgnc_symbol, one_of(rownames(COVARIATES)))
```
### Differential expression analysis
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp, fig.height=16, fig.width=25}
# Fit contrast
contrast = makeContrasts(contrasts=c(
  "BrainRegion.DiagnosisCER.Control-BrainRegion.DiagnosisCER.AD",
  "BrainRegion.DiagnosisCER.Control-BrainRegion.DiagnosisCER.PSP",
  "BrainRegion.DiagnosisCER.PSP-BrainRegion.DiagnosisCER.AD",
  "BrainRegion.DiagnosisTCX.Control-BrainRegion.DiagnosisTCX.AD",
  "BrainRegion.DiagnosisTCX.Control-BrainRegion.DiagnosisTCX.PSP",
  "BrainRegion.DiagnosisTCX.PSP-BrainRegion.DiagnosisTCX.AD"), 
                         levels = colnames(FIT$coefficients))
FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)

# Get differnetial expression
DE = list()
p = list()
for (i in 1:6){
  DE[[i]] = topTable(FIT.CONTR, coef=i, number = dim(VOOM.ADJUSTED.GENE_EXPRESSION$E)[1])
  DE[[i]] = rownameToFirstColumn(DE[[i]], 'ensembl_gene_id') %>%
    left_join(Ensemble2HGNC)
  p[[i]] <- ggplot(DE[[i]], aes(x = logFC, y = -log10(adj.P.Val))) + geom_point()
  p[[i]] <- p[[i]] + geom_hline(yintercept = -log10(0.05), color = 'red') 
  p[[i]] <- p[[i]] + ggtitle(gsub('BrainRegion.Diagnosis','',colnames(contrast)[i]))
}
multiplot(plotlist=p, cols = 3)
names(DE) = gsub('BrainRegion.Diagnosis','',colnames(contrast))

DE = plyr::ldply(DE, .id = 'Comparison')
tmp = DE %>% 
  dplyr::filter(adj.P.Val <= 0.05) %>%
  group_by(Comparison) %>%
  dplyr::summarize(nDiffExpGenes = length(unique(hgnc_symbol)))
kable(tmp)
```

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = 'UFL_Mayo_ISB Mayo Brain Bank Dickson RNASeq', parentId = parentId)
CODE <- synStore(CODE)

# Store covariates
COVARIATES = rownameToFirstColumn(COVARIATES, 'ID')
write.table(COVARIATES, file = 'covariates.tsv', sep = '\t', row.names=F, quote=F)
COV_OBJ = File('covariates.tsv', name = 'Covariates', parentId = CODE$properties$id)
COV_OBJ = synStore(COV_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)

# Store covariates
write.table(RESIDUAL.GENE_EXPRESSION, file = 'expression.tsv', sep = '\t', row.names=F, quote=F)
EXP_OBJ = File('expression.tsv', name = 'Voom Adjusted Residual Expression (BrainRegion.Diagnosis added)', parentId = CODE$properties$id)
EXP_OBJ = synStore(EXP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)

# Store differential expression results
write.table(DE, file = 'diffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('diffExpression.tsv', name = 'Differential Expression Analysis', parentId = CODE$properties$id)
DEXP_OBJ = synStore(DEXP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)
stopCluster(cl)
```
|  *Results*            |  *SynapseID*                    |
|  -------              |   ---------                     |
|  Covariates           |  `r COV_OBJ$properties$id`      |
|  Residual Expression  |  `r EXP_OBJ$properties$id`      |
|  Differential Expression  |  `r DEXP_OBJ$properties$id`      |

>>>>

---
title: "Covariate analysis of UFL-Mayo-ISB RNASeq reprocessed counts (both cerebellum and temporal cortex)"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(knit2synapse)
library(synapseClient)
library(knitr)
library(githubr)

@@

knit2synapse::knitToFolderEntity(file = "./Mayo_RNASeq_Reprocessed.Rmd",
                                 parentId = "syn5570325",
                                 entityName = 'UFL_Mayo_ISB RNASeq Reprocessed Counts')
```

@@

# library(doParallel)
# library(foreach)
# 
# cl = makeCluster(14)
# registerDoParallel(cl)

@@

thisFileName <- 'Mayo_RNASeq_Reprocessed.Rmd'

# Github link
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='AMPAD')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
# Get reprocessed paired end sample counts for temporal cortex
COUNT_TC_PE_ID <- 'syn6114408';
ALL_USED_IDs <- COUNT_TC_PE_ID
COUNT_TC_PE <- read.table(synGet(COUNT_TC_PE_ID)@filePath, header=T, sep='\t', check.names = F)

# Get reprocessed single end sample counts for temporal cortex
COUNT_TC_SE_ID <- 'syn6114409';
ALL_USED_IDs[length(ALL_USED_IDs)+1] <- COUNT_TC_SE_ID
COUNT_TC_SE <- read.table(synGet(COUNT_TC_SE_ID)@filePath, header=T, sep='\t', check.names = F)

COUNT_TC = COUNT_TC_PE + COUNT_TC_SE[rownames(COUNT_TC_PE), colnames(COUNT_TC_PE)]
colnames(COUNT_TC) = gsub('.snap','',colnames(COUNT_TC))
colnames(COUNT_TC) = gsub('11423_R0212989', '11423_TCX',colnames(COUNT_TC))
colnames(COUNT_TC) = gsub("11427_R0211812", "11427_TCX", colnames(COUNT_TC))

# Get reprocessed sample counts for cerebellum
COUNT_CE_ID <- 'syn6124945';
ALL_USED_IDs[length(ALL_USED_IDs)+1] <- COUNT_CE_ID
COUNT_CE <- read.table(synGet(COUNT_CE_ID)@filePath, header=T, sep='\t', check.names = F)

COUNT = cbind(COUNT_TC, COUNT_CE[rownames(COUNT_TC),])

@@

### Data preprocessing
```{r preprocess.data,cache=FALSE, echo=TRUE}
# Fix metadata
METADATA$AgeAtDeath = gsub("_or_above", "", METADATA$AgeAtDeath)
METADATA$Diagnosis = gsub("Pathologic Aging","Pathologic_Aging", METADATA$Diagnosis)
METADATA$BrainRegion.Diagnosis = paste(METADATA$BrainRegion, METADATA$Diagnosis, sep = '.')
METADATA$RIN2 = METADATA$RIN^2
METADATA <- METADATA %>%
  filter(!is.na(Source)) %>%
  dplyr::filter(!(ID %in% c("11386_CER","1923_CER", "11311_CER", "11477_CER", "11408_TCX", "11294_TCX", "11396_TCX")))
```
Following samples were considered outliers and removed based on PCA and/or eucledian distance:
```{r preprocess.data1}
# Match covariates to expression data
indToRetain = intersect(METADATA$ID, colnames(COUNT))
indRemoved = setdiff(colnames(COUNT), METADATA$ID)

COUNT <- COUNT[, indToRetain]

rownames(METADATA) = METADATA$ID
METADATA = METADATA[indToRetain,]
```
`r dim(COUNT)[2]` samples from `r length(unique(METADATA$Donor_ID))` subjects were obtained from the Mayo cohorts in AMP-AD reprocessed rnaseq project. Following samples were removed `r indRemoved`

@@

### Covariate clustering
Determine relationship between covariates. 
```{r covariates.clustering}
FactorCovariates <- c("Donor_ID", "Source", "Gender", "FLOWCELL", "BrainRegion.Diagnosis")
ContCovariates <- c("RIN", "RIN2", "AgeAtDeath")

@@

Clustering of initial normalised data (with NULL design)
```{r decompse.normalise.data1, fig.height=15, fig.width=10, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(VOOM.GENE_EXPRESSION$E, scale. = T, center = T)

@@

WGCNA::plotDendroAndColors(sampleTrees, 
                           labels2colors(cbind(tree,COVARIATES.tmp)),
                           groupLabels = c('Cluster',colnames(COVARIATES.tmp)))

tmp = paste('Samples in cluster 0 are', paste(sampleTrees$labels[tree == 0], collapse = ','))
tmp = base::gsub('_','\\\\_',tmp)
writeLines(tmp)
```

```{r temp, include=FALSE}
dev.off()
gc()
```

### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates is used to find significant covariates
```{r preAdjusted.covariates, results='asis', echo=FALSE}
# Find correlation between PC's of gene expression with covariates
preAdjustedSigCovars = runPCAandPlotCorrelations(VOOM.GENE_EXPRESSION$E, COVARIATES,
                                                 'NULL design(voom-normalized)',
                                                 isKeyPlot=TRUE)

@@

### Sanity Check
Residualise significant covariates using a linear model and find correlation between PCA of residuals with covariates
```{r residualSigCovars.ALL, fig.width=25, fig.height=12}
residualSigCovars[["PC_res"]][[2]]$plotData
```
Adding "BrainRegion.Diagnosis" back to the residuals
```{r addVarsBack}
varsToAddBackIn <-  grep("BrainRegion.Diagnosis", colnames(FIT$coefficients), value = T)
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION + 
  t(data.matrix(DM1$design[,varsToAddBackIn]) %*% t(FIT$coefficients[,varsToAddBackIn]))
```

### Clustering residual gene expression
```{r decompse.normalise.data3, fig.height=10, fig.width=9, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(RESIDUAL.GENE_EXPRESSION[,-(1)], scale.=T, center = T)

@@

tmp = paste('Samples in cluster 0 are', paste(sampleTrees$labels[clust == 0], collapse = ','))
tmp = base::gsub('_','\\\\_',tmp)
writeLines(tmp)
tmp = paste('Samples in cluster 3 are', paste(sampleTrees$labels[clust == 3], collapse = ','))
tmp = base::gsub('_','\\\\_',tmp)
writeLines(tmp)
tmp = paste('Samples in cluster 4 are', paste(sampleTrees$labels[clust == 4], collapse = ','))
tmp = base::gsub('_','\\\\_',tmp)
writeLines(tmp)
```

```{r temp1, include=FALSE}
gc()
dev.off()
```

@@

# Get background gene ids
backgroundGenes = data.frame(Gene.ID = rownames(COUNT), ID = rownames(COUNT)) %>%
  tidyr::separate(ID, c('ensembl_gene_id','position'), sep = '\\.')

# Query biomart
Ensemble2HGNC <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol"),
                       filters = "ensembl_gene_id", values = backgroundGenes$ensembl_gene_id,
                       mart = mart)

# Add gene names
RESIDUAL.GENE_EXPRESSION <- rownameToFirstColumn(RESIDUAL.GENE_EXPRESSION, 'Gene.ID') %>%
  left_join(backgroundGenes) %>% left_join(Ensemble2HGNC) %>%
  dplyr::select(Gene.ID, ensembl_gene_id, hgnc_symbol, one_of(rownames(COVARIATES)))

VOOM.ADJUSTED.GENE_EXPRESSION$E <- rownameToFirstColumn(VOOM.ADJUSTED.GENE_EXPRESSION$E, 'Gene.ID') %>%
  left_join(backgroundGenes) %>% left_join(Ensemble2HGNC) %>%
  dplyr::select(Gene.ID, ensembl_gene_id, hgnc_symbol, one_of(rownames(COVARIATES)))
```
### Differential expression analysis
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp, fig.height=25, fig.width=25}
# Fit contrast
contrast = makeContrasts(contrasts=c(
  "BrainRegion.DiagnosisCER.Control-BrainRegion.DiagnosisCER.AD",
  "BrainRegion.DiagnosisCER.Control-BrainRegion.DiagnosisCER.Pathologic_Aging",
  "BrainRegion.DiagnosisCER.Control-BrainRegion.DiagnosisCER.PSP",
  "BrainRegion.DiagnosisCER.Pathologic_Aging-BrainRegion.DiagnosisCER.AD",
  "BrainRegion.DiagnosisCER.PSP-BrainRegion.DiagnosisCER.AD",
  "BrainRegion.DiagnosisCER.Pathologic_Aging-BrainRegion.DiagnosisCER.PSP",
  "BrainRegion.DiagnosisTCX.Control-BrainRegion.DiagnosisTCX.AD",
  "BrainRegion.DiagnosisTCX.Control-BrainRegion.DiagnosisTCX.Pathologic_Aging",
  "BrainRegion.DiagnosisTCX.Control-BrainRegion.DiagnosisTCX.PSP",
  "BrainRegion.DiagnosisTCX.Pathologic_Aging-BrainRegion.DiagnosisTCX.AD",
  "BrainRegion.DiagnosisTCX.PSP-BrainRegion.DiagnosisTCX.AD",
  "BrainRegion.DiagnosisTCX.Pathologic_Aging-BrainRegion.DiagnosisTCX.PSP"), 
                         levels = colnames(FIT$coefficients))
FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)

# Get differnetial expression
DE = lapply(1:12, function(i, FIT.CONTR, VOOM.ADJUSTED.GENE_EXPRESSION){
  topTable(FIT.CONTR, coef=i, number = dim(VOOM.ADJUSTED.GENE_EXPRESSION$E)[1])
}, FIT.CONTR, VOOM.ADJUSTED.GENE_EXPRESSION)
names(DE) = gsub('BrainRegion.Diagnosis','',colnames(contrast))

DE = plyr::ldply(DE, .id = 'Comparison') %>%
  dplyr::mutate(Comparison1 = Comparison) %>%
  tidyr::separate(Comparison1, c('from.state','to.state'), sep = '-') %>%
  tidyr::separate(from.state, c('BrainRegion','reference'), sep = '\\.') %>%
  tidyr::separate(to.state, c('BrainRegion','against'), sep = '\\.') %>%
  tidyr::unite(Name, reference, against, sep = '-')

p <- ggplot(DE, aes(x = logFC, y = -log10(adj.P.Val))) + geom_point()
p <- p + geom_hline(yintercept = -log10(0.05), color = 'red')
p <- p + geom_vline(xintercept = log2(1.2), color = 'red')
p <- p + geom_vline(xintercept = -log2(1.2), color = 'red')
p <- p + facet_grid(BrainRegion~.+Name)
p

tmp = DE %>% 
  dplyr::filter(adj.P.Val <= 0.05) %>%
  group_by(Comparison) %>%
  dplyr::summarize(nDiffExpGenes = length(unique(genes)))
kable(tmp)
```

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = 'UFL_Mayo_ISB RNASeq Reprocessed Counts', parentId = parentId)
CODE <- synStore(CODE)

# Store covariates
COVARIATES = rownameToFirstColumn(COVARIATES, 'ID')
write.table(COVARIATES, file = 'MAYOcovariates.tsv', sep = '\t', row.names=F, quote=F)
COV_OBJ = File('MAYOcovariates.tsv', name = 'Covariates', parentId = CODE$properties$id)
COV_OBJ = synStore(COV_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)

# Raw Expression
write.table(VOOM.ADJUSTED.GENE_EXPRESSION$E, file='MAYOlogCPM.tsv', sep = '\t', row.names=F, quote=F)
RAWCPM_OBJ = File('MAYOlogCPM.tsv', 
                  name = 'Raw logCPM',
                  parentId = CODE$properties$id)
RAWCPM_OBJ = synStore(RAWCPM_OBJ,
                      used = ALL_USED_IDs, 
                      activityName = activityName, 
                      executed = thisFile, 
                      activityDescription = activityDescription)

# Store residual gene expression
write.table(RESIDUAL.GENE_EXPRESSION, file = 'MAYOexpression.tsv', sep = '\t', row.names=F, quote=F)
EXP_OBJ = File('MAYOexpression.tsv', name = 'Voom Adjusted Residual Expression (BrainRegion.Diagnosis added)', parentId = CODE$properties$id)
EXP_OBJ = synStore(EXP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)

# Store differential expression results
write.table(DE, file = 'MAYOdiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('MAYOdiffExpression.tsv', name = 'Differential Expression Analysis', parentId = CODE$properties$id)
DEXP_OBJ = synStore(DEXP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                   executed = thisFile, activityDescription = activityDescription)
stopCluster(cl)
```
|  *Results*                |  *SynapseID*                    |
|  -------                  |   ---------                     |
|  Covariates               |  `r COV_OBJ$properties$id`      |
|  Raw counts (logCPM)      |  `r RAWCPM_OBJ$properties$id`   |
|  Residual Expression      |  `r EXP_OBJ$properties$id`      |
|  Differential Expression  |  `r DEXP_OBJ$properties$id`     |
